Shades of Green

### 2023-09-26 docs/presentations/20230928-sehm_presentation.qmd
update presentation formatting

# Three Visions for a Bioeconomy

@@

## Research Questions {.fragment}

1. How innovative is the Swedish forest bioeconomy?
2. What visions of a bioeconomy are represented?
3. What eco-innovations are developed?

@@

# Data{.inverted}
```{python}
# | label: Data
n_swinno = swinno["sinno_id"].nunique()

display(
    Markdown(
        f"""
  ## SWINNO -- A Swedish Innovation Output Database with {n_swinno} Innovations{{.smaller}}

  ### [5 Year MA]{{.text-royal-blue-800}} and [Yearly]{{.text-gray-600}}
  """
    )
)

@@

@@

display(
    Markdown(
        f"# {sum_bioeconomy_innovations} Innovations in Forest Bioeconomy (Uncleaned){{.inverted}}"
    )
)

@@

# Results{.inverted}

## Count of Bioeconomy Innovation
### [5 Year MA]{.text-royal-blue-800} and [Yearly]{.text-gray-600}
```{python}
# label: fig-bioeconomy_count

## Share of Bioeconomy Innovation{.smaller}
### [5 Year MA]{.text-royal-blue-800} and [Yearly]{.text-gray-600}
```{python}

@@

## Bioeconomy Vision Classification{.smaller .scrollable}
@bugge2016WhatBioeconomyReview

|  | Biotechnology | Bioresource | Bioecology |
|---|---|---|---|
| Aim &   Objectives | Economic growth & job   creation | Economic growth &   sustainability | Sustainability, biodiversity,   conservation of ecosystems, avoiding soil degradation |
| Value   Creation | Application of biotechnology,   commercialisation of research & technology | Conversion and upgrading of   bio-resources (process oriented) | Development of integrated   production systems and high-quality products with territorial identity |
| Drivers   & mediators of innovation | R & D, patents, TTOs,   Research councils and funders (Science push, linear model) | Interdisciplinary, optimisation   of land use, include degraded land in the production of biofuels, use and   availability of bio-resources, waste management, engineering, science &   market (Interactive & networked production mode) | Identification of favourable   organic agro-ecological practices, ethics, risk, transdisciplinary   sustainability, ecological interactions, re-use & recycling of waste,   land use, (Circular and self-sustained production mode) |

<style>
  tbl {
    fontsize=9;
  }
</style>

@@

|  | Type II | Type III | Type I |
|---|---|---|---|
|  | A science-based economy driven   by industrial biotechnology<br>     <br>     The cell is a factory | Biomass replaces fossil fuels   and mining to produce energy and materials<br>     <br>     Biorefining at the heart of ecological transition (multilevel perspective). | An ecological economy, that is   compatible with the biosphere <br>     <br>     Counter-expertise rather than concrete technical solutions Criticism from   social groups who remain at the margins of decisionmaking centers |

## Preliminary Results

@@

display(
    Markdown(
        f"<span class='r-fit-text text-royal-blue-600'>{n_certain_bioeconomy_visions}</span> "
    )
)

@@

```{python}
# | output: asis

@@

>>>>

## Three Visions for a Bioeconomy

@@

## Research Questions

:::{.incremental}
1. How innovative is the Swedish forest bioeconomy?
2. What visions of a bioeconomy are represented?
3. What eco-innovations are developed?
:::

@@

# Data {.inverted}

```{python}
# | label: Data
# | output: asis

n_swinno = swinno["sinno_id"].nunique()

display(
    Markdown(
        f"## SWINNO -- A Swedish Innovation Output Database with {n_swinno} Innovations"
        + "{.smaller}"
    )
)

### [5 Year MA]{.text-royal-blue-800} and [Yearly]{.text-gray-600}

@@

## Count of Bioeconomy Innovation
###  Uncleaned [5 Year MA]{.text-royal-blue-800} and [Yearly]{.text-gray-600}

```{python}
# label: fig-bioeconomy_count

@@

display(
    Markdown(
        f"{sum_bioeconomy_innovations}{{.text-royal-blue-400}} Total Innovations in Forest Bioeconomy (Uncleaned)"
    )
)

@@

## Share of Bioeconomy Innovation{.smaller}
###  Uncleaned  [5 Year MA]{.text-royal-blue-800} and [Yearly]{.text-gray-600}
```{python}

@@

## Bioeconomy Vision Classification {.smaller}
@bugge2016WhatBioeconomyReview

|  | [Biotechnology]{.text-colorblind-green} | [Bioresource]{.text-colorblind-orange} | [Bioecology]{.text-colorblind-purple} |
|---|---|---|---|
| Aim &   Objectives | Economic growth & job   creation | Economic growth &   sustainability | Sustainability, biodiversity,   conservation of ecosystems, avoiding soil degradation |
| Value   Creation | Application of biotechnology,   commercialisation of research & technology | Conversion and upgrading of   bio-resources (process oriented) | Development of integrated   production systems and high-quality products with territorial identity |
| Drivers   & mediators of innovation | R & D, patents, TTOs,   Research councils and funders (Science push, linear model) | Interdisciplinary, optimisation   of land use, include degraded land in the production of biofuels, use and   availability of bio-resources, waste management, engineering, science &   market (Interactive & networked production mode) | Identification of favourable   organic agro-ecological practices, ethics, risk, transdisciplinary   sustainability, ecological interactions, re-use & recycling of waste,   land use, (Circular and self-sustained production mode) |
: {.tiny}

@@

|  | [Type II]{.text-colorblind-green} | [Type III]{.text-colorblind-orange} | [Type I]{.text-colorblind-purple} |
|---|---|---|---|
|  | A science-based economy driven  by industrial biotechnology| Biomass replaces fossil fuels   and mining to produce energy and materials| An ecological economy, that is compatible with the biosphere |
| | The cell is a factory | Biorefining at the heart of ecological transition (multilevel perspective). | Counter-expertise rather than concrete technical solutions <br> Criticism from  social groups who remain at the margins of decisionmaking centers |
:  {.small}

# Preliminary Results {.inverted}

@@

display(
    Markdown(
        f"## <span class='r-fit-text text-royal-blue-600'>{n_certain_bioeconomy_visions}</span> unique forest bioeconomy innovations classified"
    )
)

@@

```{python}
# | output: asis
# | include: false

@@

::: notes
39 innovations involving either a product or process innovation related to recyling. Hence, 22 innovation are associated with the bioecology vision, without using or facilitating recycling.
:::
